---
title: "Quarto Example"
author:
    - name: Nan Nourn
      email: nan@msu.edu
      orcid: 0000-0001-5057-0640
      affiliations:
        - name: Michigan State University
        - name: Department of Fisheries & Wildlife
        - name: Ecology, Evolution & Behavior Program
date: last-modified
format: html
fontsize: 0.9em
code-tools: true
code-link: true
toc: true
brand: _brand.yml
---

# Introduction

Let's create a Quarto document detailing all the ways we know how to run simple models to full Bayaesian hierarchical models with various R packages.

## Packages and Set Up

We load all the packages that we will be using. We'll be fitting our statistical models with the Stan, JAGS and NIMBLE coding languages.

```{r}
#| label: packages
#| message: false
library(rstan); library(jagsUI); library(nimble)
library(sf); library(tmap)
library(tidyverse); library(tidybayes)
library(here)
here()
theme_set(theme_minimal())
options(scipen = 10^2)
```

# Data Simulation

We simulate the data generating process to help us understand our models.

```{r}
#| label: data-sim
n <- 500
data_sim <- rnorm(n, 0 , 1)
hist(data_sim)
```

# GLMMs

# JAGS

# Stan

# Nimble

# Discussion